Differences in outcomes for patients experiencing left vs. right hemisphere ICH

### 2024-02-20 reports/aggressiveness.qmd
diagnostics and visuals done
need to do OR and ROPE stuff

---
title: Differences in care for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html: 
    mainfont: Figtree
    monofont: Source Code Pro
    fontsize: 1rem
    embed-resources: true
    toc: true
    toc-location: left
    toc-depth: 6
    toc-expand: true
    toc-title: Contents
    smooth-scroll: true
    link-external-icon: true
    link-external-newwindow: true
    code-overflow: wrap
    code-tools: true
    code-fold: true
    highlight-style: nord
---

>>>>

---
title: Differences in outcomes for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html
---

### 2024-02-20 reports/outcomes.qmd
diagnostics and visuals done
need to do OR and ROPE stuff

---
title: Differences in outcomes for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html: 
    mainfont: Figtree
    monofont: Source Code Pro
    fontsize: 0.97rem
    embed-resources: true
    toc: true
    toc-location: left
    toc-depth: 6
    toc-expand: true
    toc-title: Contents
    smooth-scroll: true
    link-external-icon: true
    link-external-newwindow: true
    code-overflow: wrap
    code-tools: true
    code-fold: true
    highlight-style: nord
---

@@

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
library(targets)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdag)
library(dagitty)
library(marginaleffects)
library(modelsummary)
library(MetBrewer)

@@

#### DAG-Implied Adjustment Sets

Similar to above, there are no

```{r outcomes dag adjustment sets}
#| code-fold: false
#| fig-align: center
#| fig.height: 10
#| fig.width: 20

adjustmentSets(
  dag_outcomes,
  type = "minimal",
  effect = "direct",
  max.results = Inf
)

adjustmentSets(
  dag_outcomes,
  type = "canonical",
  effect = "total",
  max.results = Inf
)

>>>>

---
title: Differences in outcomes for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html
---

@@

```{r setup, output=FALSE, message=FALSE, warning=FALSE}

library(targets)
library(skimr)
library(dplyr)
library(gt)
library(gtsummary)
library(ggplot2)
library(ggdag)
library(dagitty)
library(marginaleffects)
library(modelsummary)
library(MetBrewer)

@@

### 2024-02-20 reports/posteriors.qmd
diagnostics and visuals done
need to do OR and ROPE stuff

---
title: Differences in care for patients experiencing left vs. right hemisphere ICH
subtitle: Posteriors!
author: Nikhil Patel, MD
format:
  html: 
    mainfont: Figtree
    monofont: Source Code Pro
    embed-resources: true
    toc: true
    toc-location: left
    toc-depth: 6
    toc-title: Contents
    smooth-scroll: true
    link-external-icon: true
    link-external-newwindow: true
    code-overflow: wrap
    code-tools: true
    code-fold: true
    highlight-style: nord
---

```{r setup, output=FALSE, message=FALSE, warning=FALSE}
library(targets)
library(tidyverse)
library(glue)
library(marginaleffects)
library(modelsummary)
library(ggdist)
library(gghalves)
library(scales)
library(systemfonts)

@@

# posterior functions

posterior_printing <- function(x, y, var) {
  p1 <- model_parameters$priors[x]

  p2 <- y

  p3 <- predictions(y, by = "ich_laterality") |>
    as_tibble()

  p4 <- avg_comparisons(y, variables = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw)) +
    stat_halfeye(
      .width = c(0.8, 0.95), point_interval = "median_hdi",
      fill = "#bc3032"
    ) +
    scale_x_continuous(labels = label_pp) +
    labs(
      title = "Posterior Prediction",
      x = paste("Effect of hemispheric laterality\n on the probability of", {{ var }}),
      y = NULL, caption = "80% and 95% credible intervals shown in black"
    )

  return(list(
    priors = p1,
    model = p2,
    predictions = p3,
    plot = p4
  ))
}

@@

## Prior Predictive Checks

### Neurosurgical Intervention

#### Minimal Model

```{r}

posterior_printing("neurosurgery_minimal", posterior_neurosurgery_minimal, "receiving neurosurgical intervention")

#### Canonical Model

```{r}

posterior_printing("neurosurgery_canonical", posterior_neurosurgery_canonical, "receiving neurosurgical intervention")

### EVD

#### Minimal Model

```{r}

posterior_printing("evd_minimal", posterior_evd_minimal, "receiving an EVD")

#### Canonical Model

```{r}

posterior_printing("evd_canonical", posterior_evd_canonical, "receiving an EVD")

### Tracheostomy

#### Minimal Model

```{r}

posterior_printing("trach_minimal", posterior_trach_minimal, "receiving an tracheostomy")

#### Canonical Model

```{r}

posterior_printing("trach_canonical", posterior_trach_canonical, "receiving a tracheostomy")

### Days of Mechanical Ventilation

#### Minimal Model

```{r}

posterior_printing("vent_minimal", posterior_vent_minimal, "number of days of mechanical ventilation")

#### Canonical Model

```{r}

posterior_printing("vent_canonical", posterior_vent_canonical, "number of days of mechanical ventilation")

### Comfort Care

#### Minimal Model

```{r}

posterior_printing("comfort_care_minimal", posterior_comfort_care_minimal, "comfort care")

#### Canonical Model

```{r}
posterior_printing("comfort_care_canonical", posterior_comfort_care_canonical, "comfort care")

### Early WLST

#### Minimal Model

```{r}
posterior_printing("early_wlst_minimal", posterior_early_wlst_minimal, "early WLST")

#### Canonical Model

```{r}
posterior_printing("early_wlst_canonical", posterior_early_wlst_canonical, "early WLST")

### DNR

#### Minimal Model

```{r}
posterior_printing("dnr_minimal", posterior_dnr_minimal, "DNR")

#### Canonical Model

```{r}
posterior_printing("dnr_canonical", posterior_dnr_canonical, "DNR")

>>>>

---
title: Differences in outcomes for patients experiencing left vs. right hemisphere ICH
author: Nikhil Patel, MD
format:
  html
---

```{r setup, output=FALSE, message=FALSE, warning=FALSE}

library(targets)
library(tidyverse)
library(glue)
library(marginaleffects)
library(modelsummary)
library(ggdist)
library(gghalves)
library(scales)
library(systemfonts)
library(brms)
library(tidybayes)

@@

@@
